The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-27 paper/sections/results.tex
reviewer typos, removing revision colors from final version

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform a basic \emph{quantitative} comparison against FEM by measuring the deflection of the beam at its resting position as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the deflection of the SEM beams is reported as a percentage of the FEM beam's deflection.}

%\begin{wrapfigure}{l}{0.5\columnwidth}
%    	\includegraphics{figures/deflection.pdf}
%	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
%	  \label{fig:plot_beam_deflection}
%\end{wrapfigure}
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/deflection_full.pdf}
	\caption{\revise{The SEM beam deflection is plotted as a percentage of the FEM beam's deflection when the beam is at rest. As we subdivide the SEM beam, its deflection converges to the FEM beam's deflection. \ty{currently a very blank figure, which I dont mind, but could consider adding inset beam pictures to give an idea of how this experiment works}}}
  \label{fig:plot_beam_deflection}
\end{figure}

>>>>

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform a basic \emph{quantitative} comparison against FEM by measuring the deflection of the beam at equilibrium as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the deflection of the SEM beams is reported as a percentage of the FEM beam's deflection.}

%\begin{wrapfigure}{l}{0.5\columnwidth}
%    	\includegraphics{figures/deflection.pdf}
%	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
%	  \label{fig:plot_beam_deflection}
%\end{wrapfigure}
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/deflection_full.pdf}
	\caption{\revise{The SEM beam deflection is plotted as a percentage of the FEM beam's deflection when the beam is at equilibrium. As we subdivide the SEM beam, its deflection converges to the FEM beam's deflection. \ty{currently a very blank figure, which I dont mind, but could consider adding inset beam pictures to give an idea of how this experiment works}}}
  \label{fig:plot_beam_deflection}
\end{figure}
